brados: declarative, programmable object storage

### 2016-05-25 paper.tex
paper: sec3 eloquence
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\textbf{Takeway}: choosing the best implementations is dependent on both the
timing of the developemnt (Ceph Version) and the expertise of the administrator
(Ceph Features). Different versions and features of Ceph may lead the
administrator to choose a suboptimal implementation for the system's next
upgrade. The software parameters must be accounted for and benchmarked when
making design decisions.

@@

The behavior of the 1:1 implementations shows throughput drops lasting for
minutes at a time -- this limits our focus to the N:1 implementations.

 The performance of the N:1 bystestream implementation is almost identical to
the N:1 KV implementation (within 1\% mean throughput). Regardless of the true
bottleneck, it is clear that choosing the N:1 KV implementation is the better
choice because of the simple implementation and the minimal performance
degradation.

@@

This physical design process, of first thinking about the design trade-offs and
then doing parameters sweeps, is insufficient when general-purpose systems. Had
we built ZLog from the ground up (like CORFU) the story might be different but
to deal wtih the large state space we need a way to automatically and
autonomically decide which parameters to choose.

>>>>

\textbf{Takeaway}: choosing the best implementations is dependent on both the
timing of the developemnt (Ceph Version) and the expertise of the administrator
(Ceph Features). Different versions and features of Ceph may lead the
administrator to choose a suboptimal implementation for the system's next
upgrade. The software parameters must be accounted for and benchmarked when
making design decisions.

@@

The behavior of the 1:1 implementations shows throughput drops lasting for
minutes at a time -- this limits our focus to the N:1 implementations. The
performance of the N:1 bystestream implementation is almost identical to the
N:1 KV implementation (within 1\% mean throughput). Regardless of the true
bottleneck, it is clear that choosing the N:1 KV implementation is the better
choice because of the resulting implementation should be less complex and there
is minimal performance degradation.

@@

What started out as a pragmatic approach to designing a complex service on Ceph
quickly proved to be unwieldy. While finding the best solution for a specific
set of configurations (i.e. software, tunable, and hardware parameters) can be
done, finding a solution that is future-proof is still unsolved.

This physical design process, of first thinking about the design trade-offs and
then doing parameters sweeps, is insufficient for large general-purpose systems
like Ceph. Had we built ZLog from the ground up (like CORFU) the story might be
different but to deal with the large state space we need a way to automatically
and autonomically decide which parameters to choose.
